---
title: "Optimization in Supply Chain Management"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    # logo: 
    vertical_layout: fill
    social: menu
    source_code: embed
    theme: simplex
    css: www/css/custom.css

---




```{r setup, global, include=FALSE}
rm(list = ls())
library(shiny)
library(magrittr)
library(leaflet) # devtools::install_github('rstudio/leaflet')
library(highcharter) # devtools::install_github('jbkunst/highcharter')
library(plotly) # devtools::install_github('ropensci/plotly')
library(ggplot2) # devtools::install_github('hadley/ggplot2')
library(sp)
library(dplyr)
library(flexdashboard) # devtools::install_github('rstudio/flexdashboard')
library(rgeos)
library(mapproj)
library(maptools)
library(readr)
library(ggthemes)
library(knitr)
library(viridis)
library(formattable)
library(ggrepel)
library(ompr)
library(ompr.roi)
library(ROI.plugin.glpk)


source(file = "helper.R")



```


Warehouse Location
======================================================================

Sidebar {.sidebar}
-------------------------------------------------------
```{r}
hr()
strong("Application Parameters")
hr()
br()
numericInput(inputId = "grid_size", "Enter the Gird Size", value = 1000)
sliderInput(inputId = "warehouse_num", label = "Select the Number of Warehouses:", min = 10, max = 30, value = 20)
sliderInput(inputId = "customer_num", label = "Select the Number of Customers:", min = 50, max = 150, value = 100)
br()
actionButton(inputId = "solve_it", label = "  Solve  ")
hr()
```

</br>
</br>
<strong>Author: Mustafa Waheed</strong>  
[LinkedIn Profile](https://www.linkedin.com/in/mustafa-waheed-5b78552b/)   
[Github Profile](https://github.com/MustafaWaheed91)  
[Kaggle Profile](https://www.kaggle.com/mustafawaheed91)  
</br>
</br>




Row {data-width=1100}
-----------------------------------------------------------------------
### Grid Map of Customers and Warehouses
```{r}
renderPlotly({
  input$solve_it 
  if(input$solve_it == 0){
    return(ggplotly(PlotSetup(n = input$customer_num, m = input$warehouse_num, grid_size = input$grid_size)))
  } else {
    isolate({  
      withProgress(message = 'Optimization in Progress', value = 0, {
        incProgress(0.4)
        return(ggplotly(SolvedPlot(n = input$customer_num, m = input$warehouse_num, grid_size = input$grid_size)))
      })
    })
    
  }
})

```


Row
-----------------------------------------------------------------------
### Problem Background

<h4>The Warehouse Location Problem: </h4>

Given a set of customers and set of locations to build warehoses the task is to decide where to build warehouses and from what warehouses goods should be shipped to which customer.

The Two Decisions (Variable) we need to make at the same time are  
  - Where and If to build warehouses  
  - Which customer to assign to warehouses  


<strong>The Mathematical Model</strong>  

$$ Minimize  { \sum\limits_{i=1}^{n}\sum\limits_{j=1}^{m} } {TransportCost_i}{_j} * {x_i}{_j} + \sum\limits_{i=1}^{n} FixedCost_j * y_j  $$  

Subject To: 
$$ \sum\limits_{j=1}^{m} x_i{_j} {= 1} \     \  \forall  \       \   i = \{1,....,n\}$$
$$ x_i{_j} \  \ {  \leq  } \  \ y_j   \     \ { \forall}  \       \   {i = \{1,....,n\}} \  \ {j = \{1,....,m\}}$$
$$ x_i{_j} \  \ {  \in  } \  \  \{0,1\} \    \  {i = \{1,....,n\}} \  \ {j = \{1,....,m\}} \ $$
$$ y{_j} \  \ {  \in  } \  \  \{0,1\}   \      \   {j = \{1,....,m\}}$$








Vehicle Routing
======================================================================

Sidebar2 {.sidebar}
-------------------------------------------------------
```{r}
hr()
strong("Application Parameters")
hr()
br()
h4("Define Boundaris for Euclidean Space")
numericInput(inputId = "max_x", "X axis limit:", value = 500)
numericInput(inputId = "max_y", "Y axis limit:", value = 500)
sliderInput(inputId = "city_num", label = "Select the Number of Customers:", min = 1, max = 15, value = 7)
sliderInput(inputId = "driver_num", label = "Select the Number of Vehicles:", min = 1, max = 3, value = 2)
br()
actionButton(inputId = "solve_it2", label = "  Solve  ")
hr()

```



Row {data-width=1100}
-----------------------------------------------------------------------
### Grid Map of Cusomers and Delivery Depot
```{r}
renderPlotly({
  input$solve_it2 
  if(input$solve_it2 == 0){
    return(ggplotly(VrSetupPlot(n = input$city_num, m = input$driver_num, max_x = input$max_x , max_y = input$max_y )))
  } else {
    isolate({
      withProgress(message = 'Optimization in Progress', value = 0, {
        incProgress(0.4)
        return(ggplotly(VrSolvedPlot(n = input$city_num, m = input$driver_num, max_x = input$max_x , max_y = input$max_y )))
      })
    })
    
  }
})

```


Row
-----------------------------------------------------------------------
### Problem Background

<h4>The Multiple Travelling Salesman Problem: </h4>

The mTSP problem is similiar to the standard TSP but now we have more than one Vehicle.  
All salesmen start and end their trips at a single location (the depot).  
  
  
In addition, all salesmen need to visit at least one client.  

for a directed graph $$ G = (V, A) $$



<strong>The Mathematical Model</strong>  

$$ Minimize  { \sum\limits_{(i,j) \in A} } {TransportCost_i}{_j} * {x_i}{_j}  $$
Subject To: 
$$ \sum\limits_{j=2}^{n} x_1{_j} {= m} $$
$$ \sum\limits_{j=2}^{n} x_j{_1} {= m} $$
$$ \sum\limits_{i=1}^{n} x_i{_j} {= 1}   \ { \forall}  \  j = \{2,....,n\} $$
$$ \sum\limits_{j=1}^{n} x_i{_j} {= 1}   \ { \forall}  \  i = \{2,....,n\} $$
$$ x_i{_j} \  \ {  \leq  } \  \ y_j   \     \ { \forall}  \       \   {i = \{1,....,n\}} \  \ {j = \{1,....,m\}}$$
$$ x_i{_j} \  \ {  \in  } \  \  \{0,1\} \    \  \forall \  \  (i,j) \in V $$
$$ $$
$$ $$
$$ $$
$$ $$
